Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-06-09 2016_ICML/presentation/main.tex
Revising presentation

\begin{frame}{Bayesian Optimization}
Bayesian optimization\footcite{shahriari_taking_2016}:
\begin{itemize}
\item black-box optimization problems: $\mathbf{x} = \arg\max_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
\item \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
\item based on GP posterior of first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}: decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next
\item recommends $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
\item objective: minimize \emph{simple regret} 
$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$
\end{itemize}
\vspace*{2cm}
\end{frame}

@@

\begin{frame}{Experimental Setup}
Synthetic Single-Task Benchmark:
\begin{itemize}
 \item Target functions sampled from a generative model on $\mathcal{X} = [0, 1]^2$ 
 \item In practice: 
   \begin{itemize} 
   \item sample $250$ pairs $(\mathbf{x}, f(\mathbf{x}))$ from function $f \sim GP(f)$
   \item fit another GP to these pairs
   \item use resulting posterior mean as target function
   \end{itemize}
 \item Gaussian noise with standard deviation $\sigma =10^{-3}$ is added to each observation
 \item Probabilistic surrogate model used in BO:\\ GP with isotropic RBF kernel of length scale $l = 0.1$ and unit signal variance
 \pause
 \item Generative model
    \begin{itemize} 
    \item without model mismatch: GP with isotropic RBF kernel ($l = 0.1$ and unit signal variance)
    \item with model mismatch:  GP with isotropic rational quadratic kernel ($l = 0.1$, $\alpha=1.0$ and unit signal variance)
    \end{itemize}
\end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Additional content of the paper:
    \begin{itemize}
      \item Multi-task Minimum regret search
      \item results on simulated robotic task
    \end{itemize}
    \pause
    \item Future work:
    \begin{itemize}
      \item treatment of GP hyperparameters
      \item more efficient approximation techniques for MRS
    \end{itemize}
    \pause
    \item Source code available at: \url{https://github.com/jmetzen/bayesian_optimization}
  \end{itemize}

>>>>

\begin{frame}{Bayesian Optimization}
Bayesian optimization\footcite{shahriari_taking_2016} in a nutshell:
\begin{itemize}
\item black-box optimization problems: $\mathbf{x} = \arg\max_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
\item \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
\pause
\item For $n=1\dots N$:
\begin{itemize}
   \item determine GP posterior $p(f\vert \mathcal{D}_n)$ for $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ 
   \item decide on a query point based on \emph{acquisition function} $a$: $\mathbf{x}_{n+1} = \arg\max_{\mathbf{x} \in \mathcal{X}} a_{p(f\vert \mathcal{D}_n)}(x) $
\item observe (potentially noisy) $y_{n+1} = f(\mathbf{x}_{n+1}) + \epsilon$
\end{itemize}
\pause
\item recommend $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
\item objective: minimize \emph{simple regret} 
$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$
\end{itemize}
\vspace*{2cm}
\end{frame}

@@

\begin{frame}{Experimental Setup}
Synthetic Single-Task Benchmark\footcite{hennig_entropy_2012}:
\begin{itemize}
 \item Target functions sampled from a generative model on $\mathcal{X} = [0, 1]^2$ 
 \item In practice: 
   \begin{itemize} 
   \item sample $250$ pairs $(\mathbf{x}, f(\mathbf{x}))$ from function $f \sim p(f)$
   \item fit GP to these pairs
   \item use resulting posterior mean as target function
   \end{itemize}
 \item Gaussian noise with standard deviation $\sigma =10^{-3}$ is added to each observation
 \item Probabilistic surrogate model used in BO:\\ GP with isotropic RBF kernel of length scale $l = 0.1$ and unit signal variance
 \pause
 \item Generative model $p(f)$
    \begin{itemize} 
    \item without model mismatch: GP with isotropic RBF kernel ($l = 0.1$ and unit signal variance)
    \item with model mismatch:  GP with isotropic rational quadratic kernel ($l = 0.1$, $\alpha=1.0$ and unit signal variance)
    \end{itemize}
\end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Additional content of the paper:
    \begin{itemize}
      \item multi-task minimum regret search
      \item results on simulated robotic task
    \end{itemize}
    \pause
    \item Future work:
    \begin{itemize}
      \item treatment of GP hyperparameters
      \item more efficient approximation techniques for MRS
    \end{itemize}
    \pause
    \item Source code available at: \url{https://github.com/jmetzen/bayesian_optimization}
  \end{itemize}
